Topological Equivariant Artist Model

### 2022-02-18 slides/main.tex
implementation construction

    \begin{block}{Data Transformations}
    $\dfuncc:\dtotalc\restriction_{\dbasepointc} \rightarrow \dtotalc\restriction_{\dbasepointc} \in Hom(\dfiberc\restriction_{\dbasepointc},\dfiberc\restriction_{\dbasepointc})$ 
    \end{block} 
\end{frame}

@@

\begin{frame}{complex data}
    \begin{description}[style=newline]
        \item[combining continuities]{given $\dbasepointc_{a} \in \dbasec_{c} \subset \dbasec_{a}$ and $\dbasepointc_{b} \in \dbasec_{c} \subset \dbasec_{b}$, if $\dbasepointc_{a} = \dbasepointc_{b}$ then $\equivc(\dsectionc(\dbasepointc_{a})) = \equivc(\dsectionc(\dbasepointc_{b}))$ for all $\dbasepointc_{a}, \dbasepointc_{b} \in \dbasec_{a}\bigsqcup\limits_{\dbasec_{c}} \dbasec_{b}$}
        \item[shared fibers]{
            if $p = p^{\prime}$ then $\equivc \circ q$ = $\equivc^{\prime} \circ q^{\prime}$
        \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
        \& \dfiberc^a \times \dfiberc^b 
        \arrow[ld, "p"', color=fiber] 
        \arrow[rd, "q \circ \equivc"] \&     \\
        \dfiberc^a \& \& M^a \\
        \& \dfiberc^a \times \dfiberc^c 
        \arrow[lu, "p^{\prime}", color=fiber] 
        \arrow[ru, " q^{\prime} \circ\equivc^{\prime}"'] \&    
      \end{tikzcd}
    \end{equation*}}         
        \item[both]{given $\dsectionc^{a} \in \sheafc_{\dbasec_a, \dtotalc_a}, \dsectionc^{b} \in \sheafc_{\dbasec_b, \dtotalc_b}$ and $\dbasepointc \in \dbasec_{a}\bigsqcup\limits_{\dbasec_{c}} \dbasec_{b}$ then $q(\equivc(\dsection^a(\dbasepointc))) = q^{\prime}(\equivc(\dsectionc^b(\dbasepointc)))$ when $p(\dfiberc^{a}\restriction_{\dbasepointc}) = p^{\prime}(\dfiberc^{b}\restriction_{\dbasepointc})$}
    \end{description}
\end{frame}

@@

    \begin{alertblock}{Build in Equivariance}
    implement $\vchannelc: \dsectionc \mapsto \vsectionc$ as a monoid homomorphism $\vchannelc: \dfuncc_{\dtotalc} \rightarrow \dfuncc_{\vtotalc}$ such that 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ 
    \end{description} 
\end{alertblock}
\end{frame}

\begin{frame}{Sample $\dfuncc$: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
    \begin{table}[H]
        \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
            \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
            nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
            ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
            interval &  translation &  $\vchannel (\delement + c) = \vchannel(\delement) + c$ \\
            ratio &  scaling &  $\vchannel(\delement* c) = \vchannel(\delement)*c $\\ \bottomrule
        \end{tabularx}
    \end{table}
\end{frame}

\begin{frame}{Shared Components: $\vchannelc = \prod\limits_{i=0}^{n}\vchannelc_i$}
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiberc_a\times \dfiberc_b 
            \arrow[rr, "\vchannelc"] 
            \arrow[rd, "p_{\dfiberc}"] \& \& \vfiberc_a\times \vfiberc_b 
            \arrow[rd, "p_{\vfiberc}"] \& \\    \& \dfiberc_{a} \arrow[rr, "\vchannelc_{a}", dashed] \& \& \vfiberc_a \\
            \dfiberc_a\times \dfiberc_c 
            \arrow[rr, "\vchannelc^{\prime}"] \arrow[ru, "p_{\dfiberc^{\prime}}"'] \& \& {\vfiberc_a}^{\prime}\times {\vfiberc_c}^{prime} \arrow[ru, "p_{\vfiberc^{\prime}}"'] \&           
            \end{tikzcd}
    \end{equation}
    \begin{alertblock}{Consistent Transformations \cite{hullmanKeeping2018}}
        if $p_{\dfiberc} = p_{\dfiberc^{\prime}}$ then $p_{\vfiberc}(\vchannelc(\dsectionc)) = p_{\vfiberc^{\prime}}(\vchannelc^{\prime}(\dsectionc^{\prime}))$ s.t. there exists a transformation $\vchannelc_a: \dfiberc_{a}\rightarrow \vfiberc_{a}$
    \end{alertblock}
\end{frame}

@@

>>>>

    \begin{block}{Data Transformations}
    $\dfuncc:\dtotalc\restriction_{\dbasepointc} \rightarrow \dtotalc\restriction_{\dbasepointc^{\prime}} \in Hom(\dfiberc\restriction_{\dbasepointc},\dfiberc\restriction_{\dbasepointc^{\prime}})$ 
    \end{block} 
\end{frame}

@@

\begin{frame}{Complex data}
    \begin{description}[style=newline]
        \item[combining continuities]{given $\dbasepointc_{a} \in \dbasec_{c} \subset \dbasec_{a}$ and $\dbasepointc_{b} \in \dbasec_{c} \subset \dbasec_{b}$, if $\dbasepointc_{a} = \dbasepointc_{b}$ then $\equivc(\dsectionc(\dbasepointc_{a})) = \equivc(\dsectionc(\dbasepointc_{b}))$ for all $\dbasepointc_{a}, \dbasepointc_{b} \in \dbasec_{a}\bigsqcup\limits_{\dbasec_{c}} \dbasec_{b}$}
        \item[shared fibers]{
            if $p = p^{\prime}$ then $\equivc \circ q$ = $\equivc^{\prime} \circ q^{\prime}$
        \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
        \& \dfiberc^a \times \dfiberc^b 
        \arrow[ld, "p"', color=fiber] 
        \arrow[rd, "q \circ \equivc"] \&     \\
        \dfiberc^a \& \& M^a \\
        \& \dfiberc^a \times \dfiberc^c 
        \arrow[lu, "p^{\prime}", color=fiber] 
        \arrow[ru, " q^{\prime} \circ\equivc^{\prime}"'] \&    
      \end{tikzcd}
    \end{equation*}}         
        \item[both]{given $\dsectionc^{a} \in \sheafc_{\dbasec_a, \dtotalc_a}, \dsectionc^{b} \in \sheafc_{\dbasec_b, \dtotalc_b}$ and $\dbasepointc \in \dbasec_{a}\bigsqcup\limits_{\dbasec_{c}} \dbasec_{b}$ then $q(\equivc(\dsection^a(\dbasepointc))) = q^{\prime}(\equivc(\dsectionc^b(\dbasepointc)))$ when $p(\dfiberc^{a}\restriction_{\dbasepointc}) = p^{\prime}(\dfiberc^{b}\restriction_{\dbasepointc})$}
    \end{description}
\end{frame}

@@

    \begin{alertblock}{Build in Equivariance}
    implement $\vchannelc$ as a functor such that 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ \note{for all sections} 
    \end{description} 
\end{alertblock}
\end{frame}

\begin{frame}{Sample $\dfuncc$: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
    \begin{table}[H]
        \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
            \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
            nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
            ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
            interval &  translation &  $\vchannel (\delement + c) = \vchannel(\delement) + \vchannel(c)$ \\
            ratio &  scaling &  $\vchannel(\delement* c) = \vchannel(\delement)*\vchannel(c) $\\ \bottomrule
        \end{tabularx}
    \end{table}
\end{frame}

\begin{frame}{Shared Components: $\vchannelc = \prod\limits_{i=0}^{n}\vchannelc_i$}
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiberc_a\times \dfiberc_b 
            \arrow[rr, "\vchannelc"] 
            \arrow[rd, "p_{\dfiberc}"] \& \& \vfiberc_a\times \vfiberc_b 
            \arrow[rd, "p_{\vfiberc}"] \& \\    \& \dfiberc_{a} \arrow[rr, "\vchannelc_{a}", dashed] \& \& \vfiberc_a \\
            \dfiberc_a\times \dfiberc_c 
            \arrow[rr, "\vchannelc^{\prime}"] \arrow[ru, "p_{\dfiberc^{\prime}}"'] \& \& {\vfiberc_a}^{\prime}\times {\vfiberc_c}^{\prime} \arrow[ru, "p_{\vfiberc^{\prime}}"'] \&           
            \end{tikzcd}
    \end{equation}
    \begin{alertblock}{Consistent Transformations \cite{hullmanKeeping2018}}
        if $p_{\dfiberc} = p_{\dfiberc^{\prime}}$ then $p_{\vfiberc}(\vchannelc(\dsectionc)) = p_{\vfiberc^{\prime}}(\vchannelc^{\prime}(\dsectionc^{\prime}))$ s.t. there exists a transformation $\vchannelc_a: \dfiberc_{a}\rightarrow \vfiberc_{a}$
    \end{alertblock}
\end{frame}

\begin{frame}{Remapping Components}
    \begin{block}<>{Functor $\vchannel$}
        $\vchannelc$ is a functor from on fiber categories $\vchannel: \mathcal{\dfiberc} \rightarrow \mathcal{\vfiberc}$

    \end{block}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiberc 
            \arrow[rr, "\vchannelc_{\dfiberc}"] 
            \arrow[rrdd, "{\vchannelc_{\dfiberc}}^{\prime}"', dotted] 
            \&  \& 
            \vfiberc \coloneqq \dfiberc^{\prime}  
            \arrow[dd, "\vchannelc_{\vfiberc}"] \\
            \&  \& \\
            \&  \& \vfiberc^{\prime}                           
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

\begin{frame}{implement}
    \begin{tikzcd}[ampersand replacement = \&]
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
    \arrow[r, "\vchannelc"] \& 
    \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} 
    \arrow[r, "\vmarkc_*"] 
    \arrow[rr, "\vmarkc", bend left] \& 
    \cgamma{\opensetc}{\gtotalc\restriction_{\opensetc}} \& 
    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
    \arrow[l, "\vindexcpush"]\\ 
    \& \\ \& 
    \opensetc 
    \arrow[luu, "{\sheafc_{\dbasec, \dtotalc}}" description, maps to] 
    \arrow[uu, "{\sheafc_{\dbasec, \vtotalc}}" description, maps to] 
    \arrow[ruu, "{\sheafc_{\dbasec, \gtotalc}}" description, maps to] 
    \& \& 
    \opensetgc \arrow[uu, "{\sheafc_{\gbasec, \gtotalc}}" description, maps to] 
    \arrow[ll, "\vindexc"', dashed]
    \end{tikzcd}
\end{frame}
